---
output: html_document
editor_options: 
  chunk_output_type: console
execute: 
  warning: false
page-layout: full
format:
  html:
    code-fold: true
    code-summary: "Show the code"
bibliography: references.bib
---

```{r}
#| label: load-libraries

library(tidyverse)
library(lme4)

```

```{r}
#| label: load-data

dat <- read_csv("data-synthetic/synDiary.csv")
nin <- read_csv("data-synthetic/synNintendo.csv")
xbox <- read_csv("data-synthetic/synXbox.csv")
```


## H1. Greater in-game need satisfaction is associated with greater global need satisfaction (H6 in BANG)

```{r}
#| label: h1-model

h1mod <- lmer(globalNS ~ gameNS_cw + gameNS_cb + age + gender + eduLevel + employment + (1 + gameNS_cw|id), data = dat)

```


## H2b. Situational need satisfaction is positively associated with higher likelihood of playing in the period after survey completion (H8 in BANG)

```{r}
#| label: h2a-model


```



## H2b. Global need frustration is associated with higher likelihood of playing in the period after survey completion (H9 in BANG)

```{r}
#| label: h2b-model


```


## H3. When gaming displaces a core life domain (work/school, social engagements, sleep/eating/fitness, or caretaking), global need satisfaction will be lower (H5 in BANG)


```{r}
#| label: h3-model


```
